Recover time to reference state: <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-17 R/model_fcs_markdown.Rmd
Update

```{r}
iter = 10000
chains = 4
thin = 2
priors <- c(
  set_prior("normal(0, 1)", class = "b"),
  set_prior("normal(0.1, 1)", class = "b", coef = "sand_ratio25"),
  set_prior("normal(0.2, 1)", class = "b", coef = "sand_ratio50"),
  set_prior("normal(0.1, 1)", class = "b", coef = "expositionsouth"),
  set_prior("normal(0.1, 1)", class = "b", coef = "survey_year_fct2019"),
  set_prior("normal(0.2, 1)", class = "b", coef = "survey_year_fct2020"),
  set_prior("normal(0.3, 1)", class = "b",coef = "survey_year_fct2021"),
  set_prior("cauchy(0, 1)", class = "sigma")
)
```

@@

```{r}
load(file = here("outputs", "models", "model_fcs_1.Rdata"))
load(file = here("outputs", "models", "model_fcs_2.Rdata"))
load(file = here("outputs", "models", "model_fcs_3.Rdata"))
```

@@

```{r}
m_1 <- m1
m_2 <- m3
m_1$formula
m_2$formula
```

@@

##### LOO-PIT plots

```{r}
p1 <- ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
p2 <- ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
p1 / p2
plot(loo1)
plot(loo2)
```

@@

```{r}
prior_summary(m_2, all = FALSE)
```

@@

```{r}
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```

@@

```{r}
draws2
mcmc_intervals(
  posterior1,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
)
mcmc_intervals(
  posterior2,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
)
```

@@

```{r}
(emm <- emmeans(m_2, revpairwise ~ target_type + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
```

>>>>

```{r}
iter = 10000
chains = 4
thin = 2
seed = 123
priors <- c(
  set_prior("normal(0, 1)", class = "b"),
  set_prior("normal(0.1, 1)", class = "b", coef = "sand_ratio25"),
  set_prior("normal(0.2, 1)", class = "b", coef = "sand_ratio50"),
  set_prior("normal(0.1, 1)", class = "b", coef = "expositionsouth"),
  set_prior("normal(0.1, 1)", class = "b", coef = "survey_year_fct2019"),
  set_prior("normal(0.2, 1)", class = "b", coef = "survey_year_fct2020"),
  set_prior("normal(0.3, 1)", class = "b",coef = "survey_year_fct2021"),
  set_prior("cauchy(0, 1)", class = "sigma")
)
```

@@

```{r}
load(file = here("outputs", "models", "model_fcs_2.Rdata"))
load(file = here("outputs", "models", "model_fcs_full.Rdata"))
```

@@

```{r}
m_1 <- m2
m_2 <- m_full
m_1$formula
m_2$formula
```

@@

##### LOO Leave one out

```{r}
loo1
loo2
plot(loo1)
plot(loo2)
```

Leave one out probability integral transform

```{r}
p1 <- ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
p2 <- ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
p1 / p2

@@

```{r}
prior_summary(m_1, all = FALSE)
```

@@

```{r}
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```

@@

```{r}
draws2
mcmc_intervals(
  posterior1,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
mcmc_intervals(
  posterior2,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

@@

```{r}
(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
```

### 2022-11-17 R/model_persistence_markdown.Rmd
Update

---
title: "Persistence of seed mixture species: <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "Markus Bauer <br>"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
#output: github_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "pdf") })
---

@@

```{r}
sites <- read_csv(
  here("data", "processed", "data_processed_sites_temporal.csv"),
  col_names = TRUE, na = c("na", "NA", ""), col_types =
    cols(
      .default = "?",
      plot = "f",
      site = "f",
      sand_ratio = "f",
      substrate_depth = "f",
      target_type = col_factor(levels = c(
        "dry_grassland", "hay_meadow"
      )),
      seed_density = "f",
      exposition = col_factor(levels = c(
        "north", "south"
      )),
      survey_year = "c"
    )
  ) %>%
  ### Exclude data of seed mixtures
  filter(presabu == "presence") %>%
  mutate(
    survey_year_fct = factor(survey_year),
    id = factor(id),
    n = persistence
  ) %>%
  select(
    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
    seed_density, survey_year_fct, survey_year, n
  )
```

@@

```{r echo = FALSE}
plot1 <- ggplot(sites %>% filter(survey_year == 2021),
                aes(y = n, x = sand_ratio)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Sand ratio [vol%] (Data of 2021)")
plot2 <- ggplot(sites %>% filter(survey_year == 2021),
                aes(y = n, x = substrate_depth)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Substrate depth [cm] (Data of 2021)")
plot3 <- ggplot(sites %>% filter(survey_year == 2021),
                aes(y = n, x = target_type)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Target type (Data of 2021)")
plot4 <- ggplot(sites %>% filter(survey_year == 2021),
                aes(y = n, x = seed_density)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Seed density [g/m²] (Data of 2021)")
(plot1 + plot2) / (plot3 + plot4)
plot1 <- ggplot(sites %>% filter(survey_year == 2021),
                aes(y = n, x = exposition)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Exposition (Data of 2021)")
plot2 <- ggplot(sites, aes(y = n, x = survey_year_fct)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Survey year")
plot3 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = site)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Blocks (Data of 2021)")
(plot1 + plot2) / (plot3)
ggplot(data = sites,
       aes(x = sand_ratio, y = n, color = target_type)) + 
  geom_quasirandom(alpha = 0.5, dodge.width = 0.8) +
  geom_boxplot(fill = "transparent") +
  facet_grid(exposition ~ survey_year_fct) +
  labs(title = "Target type vs. sand ratio [vol%]")
ggplot(data = sites,
       aes(x = sand_ratio, y = n, color = substrate_depth)) + 
  geom_quasirandom(alpha = 0.5, dodge.width = 0.8) +
  geom_boxplot(fill = "transparent") +
  facet_grid(exposition ~ survey_year_fct) +
  labs(title = "Substrate depth [cm] vs. sand ratio [vol%]")
ggplot(data = sites,
       aes(x = seed_density, y = n, color = target_type)) + 
  geom_quasirandom(alpha = 0.5, dodge.width = 0.8) +
  geom_boxplot(fill = "transparent") +
  facet_grid(exposition ~ survey_year_fct) +
  labs(title = "Target type vs. Seed density [g/m²]")
```

@@

##### LOO-PIT plots

>>>>

---
title: "Persistence of seed mixture species: <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "Markus Bauer <br>"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: github_document
---

@@

```{r}
sites <- read_csv(
  here("data", "processed", "data_processed_sites_temporal.csv"),
  col_names = TRUE, na = c("na", "NA", ""), col_types =
    cols(
      .default = "?",
      plot = "f",
      site = "f",
      sand_ratio = "f",
      substrate_depth = col_factor(levels = c("30", "15")),
      target_type = col_factor(levels = c(
        "hay_meadow", "dry_grassland"
      )),
      seed_density = "f",
      exposition = col_factor(levels = c(
        "north", "south"
      )),
      survey_year = "c"
    )
  ) %>%
  ### Exclude data of seed mixtures
  filter(presabu == "presence") %>%
  mutate(
    survey_year_fct = factor(survey_year),
    id = factor(id),
    n = persistence
  ) %>%
  select(
    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
    seed_density, survey_year_fct, survey_year, n
  )
```

@@

```{r echo = FALSE}
plot1 <- ggplot(sites %>% filter(survey_year == 2021),
                aes(y = n, x = sand_ratio)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  facet_grid(~ survey_year_fct) +
  labs(title = "Sand ratio [vol%]")
plot2 <- ggplot(sites %>% filter(survey_year == 2021),
                aes(y = n, x = substrate_depth)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  facet_grid(~ survey_year_fct) +
  labs(title = "Substrate depth [cm]")
plot3 <- ggplot(sites %>% filter(survey_year == 2021),
                aes(y = n, x = target_type)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  facet_grid(~ survey_year_fct) +
  labs(title = "Target type")
plot4 <- ggplot(sites %>% filter(survey_year == 2021),
                aes(y = n, x = seed_density)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  facet_grid(~ survey_year_fct) +
  labs(title = "Seed density [g/m²]")
(plot1 + plot2) / (plot3 + plot4)
plot1 <- ggplot(sites %>% filter(survey_year == 2021),
                aes(y = n, x = exposition)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  facet_grid(~ survey_year_fct) +
  labs(title = "Exposition")
plot2 <- ggplot(sites, aes(y = n, x = survey_year_fct)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Survey year")
plot3 <- ggplot(sites %>% filter(survey_year == 2021), aes(y = n, x = site)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  facet_grid(~ survey_year_fct) +
  labs(title = "Blocks")
plot4 <- ggplot(sites, aes(y = n, x = botanist_year)) +
  geom_quasirandom(color = "grey") + geom_boxplot(fill = "transparent") +
  labs(title = "Botanists and survey year") +
  theme(axis.text.x = element_text(angle = 90))
(plot1 + plot2) / (plot3 + plot4)
ggplot(data = sites,
       aes(x = sand_ratio, y = n, color = target_type)) + 
  geom_quasirandom(alpha = 0.5, dodge.width = 0.8) +
  geom_boxplot(fill = "transparent") +
  facet_grid(exposition ~ survey_year_fct) +
  labs(title = "Target type vs. sand ratio [vol%]")
ggplot(data = sites,
       aes(x = sand_ratio, y = n, color = substrate_depth)) + 
  geom_quasirandom(alpha = 0.5, dodge.width = 0.8) +
  geom_boxplot(fill = "transparent") +
  facet_grid(exposition ~ survey_year_fct) +
  labs(title = "Substrate depth [cm] vs. sand ratio [vol%]")
ggplot(data = sites,
       aes(x = seed_density, y = n, color = target_type)) + 
  geom_quasirandom(alpha = 0.5, dodge.width = 0.8) +
  geom_boxplot(fill = "transparent") +
  facet_grid(exposition ~ survey_year_fct) +
  labs(title = "Target type vs. Seed density [g/m²]")
```

@@

##### LOO-PIT: Leave one out probability integral transform checks

### 2022-11-17 R/model_recovery_time_markdown.Rmd
Update

```{r}

>>>>

```{r}
sites <- read_csv(
  here("data", "processed", "data_processed_sites_nmds.csv"),
  col_names = TRUE, na = c("na", "NA", ""),
  col_types = cols(
    .default = "?",
    id = "f",
    plot = "f",
    site = "f",
    exposition = col_factor(levels = c("north", "south",
                                       "other")),
    sand_ratio = "f",
    substrate_depth = col_factor(levels = c("30", "15")),
    target_type = col_factor(
      levels = c("hay_meadow", "dry_grassland", "other")
      ),
    seed_density = "f"
    )
  ) %>%
  filter(reference == "2018" | reference == "2019" | reference == "2020" |
           reference == "2021") %>%
  mutate(
    survey_year_fct = factor(survey_year),
    survey_year = as.numeric(survey_year),
    botanist_year = str_c(survey_year, botanist, sep = " "),
    n = recovery_time
    )
```
